---
title: "Correlation between Primary Tumor Location and Age in nonsmokers"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


BSMS222 
Jihyun Seo(2015250126)


## 1. Introduction


In resource paper 'Proteogenomics of Non-smoking Lung Cancer in East Asia Delineates Molecular Signature of Pathogenesis and Progression', focusing on clinical data from Taiwan(TW) cohort, what I was wondering is about primary tumor location in treatment-naive patients from TW, especially whose histology type is ADC(adenocacinoma) and who are nonsmokers. Which factor among paients' characters such as age, gender, ADC stage or EGFR_status would have correlation to tumor location?


Description of tumor location in lung. 
RUL = Right Upper Lobe, RML = Right Middle Lobe, RLL = Right Lower Lobe
LUL = Left Upper Lobe, LLL = Left Lower Lobe




## 2. Dataset $ Visualizing

```{r}
library(dplyr)
library(ggplot2)
library(readxl)
library(tidyverse)
```

```{r}
d1 <- read_excel("mmc1.xlsx", sheet = "Table S1A_clinical_103patient")
head(d1)
```


First of all, select data of only nonsmokers and ADC patients from the clinical data source given from paper.


```{r}
d2 <- d1 %>% filter(`Smoking Status` == 'Nonsmoke', `Histology Type` == "ADC")
```



```{r}
d2 %>% ggplot(aes(`Primary Tumor Location`, Age)) + 
  geom_boxplot() + 
  geom_point(alpha=0.3, size = 1.5)
```

1) gender and tumor location 2) stage and tumor location 3) EGFR_Status and tumor location 4) age and tumor location
I thought these 4 points of view and among these, 4)age and tumor location had meaningful correlation.




## 3. Discussion

According to the figure, in left lung lobes, median of upper lobe was higher in age than one of lower lobe. Likewise in right lung lobes, median of upper part was the highest, followed by middle part and then lower part. 
In terms of median, left and right lungs both look right-top direction and it leads to positive correlation between age and location of ADC(upper-middle-lower). 



## 4. Reference

Yi-JuChen, Theodoros I.Roumeliotis, Ya-Hsuan Chang, Ching-Tai Chen, Chia-Li Han, Miao-Hsia Lin, Huei-Wen Chen , Gee-Chen Chang, Yih-Leong Chang, Chen-Tu Wu, Mong-Wei Lin, Min-Shu Hsieh, Yu-Tai Wang, Yet-Ran Chen, Inge Jonassen, Fatemeh Zamanzad Ghavidel, Ze-Shiang Lin, Kuen-Tyng Lin1 …Yu-Ju Chen, Proteogenomics of Non-smoking Lung Cancer in East Asia Delineates Molecular Signatures of Pathogenesis and Progression, Cell, Volume 182, Issue 1, 9 July 2020, Pages 226-244.e17